\begin{rubric}{Miscellaneous Experience}
\subrubric{Awards and Achievements}
\entry*[2022] \textbf{Outstanding Merit Scholarship}, Awarded to the 3 best university students residents in Oliveira do Hospital.
%
\entry*[2022] \textbf{Finalist in the Digital Health category}, Hackaton Tecstorm 2022.
%
\entry*[2021] \textbf{Merit Award}, Top Bachelor Finalist, School of Technology and Management of Oliveira do Hospital.
%
\entry*[2021] \textbf{Second Place in the category 5G of the Future}, Hackaton Tecstorm 2021.

\subrubric{Certification}
\entry*[2023] \textbf{CCSK v4.1 Foundation Training}. Awarded by Cloud Security Alliance.
\entry*[2023] \textbf{IoT Fundamentals: Connecting Things}. Awarded by Cisco.
\entry*[2023] \textbf{Networking Academy Learn-A-Thon 2023}. Awarded by Cisco.
\entry*[2023] \textbf{Introduction to IoT}. Awarded by Cisco.
\entry*[2022] \textbf{CLA: Programming Essentials in C}. C++ Institute.
\entry*[2022] \textbf{Network Security}. Awarded by Cisco.
\entry*[2021] \textbf{CyberOps Associate}. Awarded by Cisco.
\entry*[2021] \textbf{Cybersecurity Essentials}. Awarded by Cisco.
\entry*[2021] \textbf{Introduction to Cybersecurity}. Awarded by Cisco.
\entry*[2021] \textbf{IoT Fundamentals: IoT Security}. Awarded by Cisco.
\entry*[2021] \textbf{JSE: Javascript Essentials 1}. Awarded by Javascript Institute.
\entry*[2021] \textbf{CCNA: Enterprise Networking, Security, and Automation}. Awarded by Cisco.
\entry*[2021] \textbf{CCNA: Switching, Routing, and Wireless Essentials}. Awarded by Cisco.
\entry*[2021] \textbf{PCAP: Programming Essentials in Python}. Awarded by Python Institute.
\entry*[2020] \textbf{CCNA: Introductions to Networks}. Awarded by Cisco.
\entry*[2018] \textbf{NDG Linux Essentials}. Awarded by Linux Professional Institute.

\end{rubric}